---
title: "creative-data-visualization"
author: "SLCornett"
class: "ANT388 Applied Data Analysis"
output: 
  output: 
  html_document: 
    theme: darkly
    highlight: textmate
    code_folding: show
    toc: yes
    toc_float: yes
    toc_depth: 4
    fig_width: 8
---
```{r setup, include=FALSE}
# These are some {knitr} options I typically use to format my ***RMarkdown*** documents in a consistent way
# You should feel free to alter these or use other "chunk options" as you see fit!
# Sometimes, for example, you might want to suppress warnings or
# messages, and that behavior can be set for specific code chunks in
# the chunk header, e.g., ```{r warning = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  eval = TRUE, # run code in code chunks
  echo = TRUE, # render output of code chunks
  warning = TRUE, # do not suppress "warnings"
  message = TRUE, # do not suppress "messages"
#  comment = "##", # prefix for comment lines
#  prompt = ">", # prefix for code lines
  tidy = TRUE,
  tidy.opts = list(blank = FALSE, width.cutoff = 75),
  fig.path = "images/", # name of folder for images
  fig.align = "center" # centers any images on the page
)
```

# Creative Data Visualization: Electrophysiology Data

```{r preliminaries, message=FALSE, warning=FALSE}
require(tidyverse)
require(ggplot2)
# from github
devtools::install_github("cutterkom/generativeart")
require(generativeart)
```

```{r load in gssg oxidation dataset}
f1 <- "https://raw.githubusercontent.com/slcornett/creative-data-visualization/main/data/2018-04-05_GSSG_Oxidation.csv"
gssg <- read_csv(f1,  col_names = TRUE)
head(gssg)
gssg_p1 <- ggplot(data = gssg, aes(x = time_s, y = GSSG_Current_µA)) +
  geom_jitter()
gssg_p1
```


